Supplemental Information

### 2024-03-03 script/CoverLetter.Rmd
making submission docs

\begin{flushleft}
Dr. Aaron Ellison \newline
Executive Editor \newline
Methods in Ecology and Evolution \newline
\end{flushleft}

@@

In this paper, we combine Hyb-Seq to generate *de novo* sequence databases, informed by museum records, and species distribution modelling. 
Further we use the results of phenological modelling to interpret our sequence alignment results to increase the likelihood of accurate results.

@@

We believe that the use of the Angiosperms353 probes was novel at the inception of the study, and that several manuscripts utilizing them will be forthcoming to a variety of journals.

Our submission contains X supplementary materials, X figures and X tables. It unfortunately is currently at roughly 9,300 words. 
However *circa* 900 words are dedicated to a plain text overview of the methods, a section which we believe elucidates the integration of the various approaches, and clarifies adoption by subsequent users. 
Considerable length is dedicated to the methods, which contain five years of field work, and similarly thorough microscopy, and molecular work; but which we have cut by nearly 500 words.

We have no conflicts of interest to disclose. Additionally, this work - nor any part of it - has been submitted to any other journal.

>>>>

\begin{flushleft}
Dr. Aaron Ellison \newline
Executive Editor \newline
Methods in Ecology and Evolution \newline
Senior Research Fellow in Ecology \textit{Emeritus} \newline
Harvard Forest \newline
\end{flushleft}

@@

In this paper we develop an intuitive approach to generate plant reference sequence databases tailored to specific areas for metabarcoding projects, as well as a lens to critically evaluate metagenomic results using phenological data.
This spatio-temporal approach utilizes, among other sources - museum and citizen science records, species distribution modelling, and the weibull distribution, to create baseline environmental data in an approach which is globally applicable.
Further we use bait-capture, via the popular Angiosperms 353 probes, as our method to generate sequence reads for metabarcoding.

@@

We believe that the use of the Angiosperms353 probes was novel at the inception of the study, and are aware of several manuscripts utilizing them which will be forthcoming in a variety of journals.

Our submission contains X supplementary materials, X figures and X tables. It unfortunately is currently at roughly 8,900 words. 
However *circa* 900 words are dedicated to a plain text overview of the methods, a section which we believe elucidates the integration of the various approaches, and clarifies adoption by subsequent users. 
Considerable length is dedicated to the methods, which contain five years of field work, and similarly thorough microscopy, and molecular work; but which we have cut by nearly 1000 words.
The full details or our methods are provided as supplementary materials.

We have no conflicts of interest to disclose. Additionally, this work - nor any part of it - has been submitted to any other journal. Although, it is cited and discussed in our Grimes Review which is currently in review for *Journal of Ecology*.

### 2024-03-03 script/SupplementaryInformation.Rmd
making submission docs

```{r, include=FALSE}
knitr::opts_chunk$set(
  comment = "#>", echo = FALSE, fig.width = 6
)
```

@@

# Table S1
```{r}
knitr::kable(df, caption = info, col.names = c('Variable', 'Data Source', 'Geographic Extent'), booktabs = TRUE) |> 
  kableExtra::row_spec(0,bold=TRUE) |>
  kableExtra::collapse_rows(1) |>
  kableExtra::kable_styling(latex_options="scale_down") |>
  kableExtra::add_footnote('CONUS; CONtinental United States')

@@

```{r Voucher Reference Specimen table 1, echo = F}
knitr::include_graphics('../graphics/tables/specimen_tables-1.pdf')
```

```{r Voucher Reference Specimen table 2, echo = F}
knitr::include_graphics('../graphics/tables/specimen_tables-2.pdf')
```

>>>>

```{r, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
```

@@

```{r}
knitr::kable(
  df, 
  caption = info, 
  col.names = c('Variable', 'Data Source', 'Geographic Extent'),
  booktabs = TRUE, 
  format  = "latex",
  longtable = FALSE
  ) |> 
  kableExtra::row_spec(0,bold=TRUE) |>
  kableExtra::collapse_rows(1) |>
  kableExtra::kable_styling(latex_options="scale_down") |>
  kableExtra::add_footnote('CONUS; CONtinental United States')

@@

```{r Voucher Reference Specimen table 1, echo = F}
knitr::include_graphics('../graphics/tables/specimen_table_v2.png')
```
